%------------------------------------------------------------------------------
\chapter*{Acknowledgements}
\label{sec:ack}
%------------------------------------------------------------------------------
This work would not have been possible without the support and guidance of many people.
First and foremost, I would like to express my sincere thanks to my supervisor Prof.\ Dr.\ Jens Lehmann for his constant guidance and support throughout the PhD studies.
At the same time, I am also greatly appreciated by his kindness, patience, and encouragement that let me feel more confident and grow gradually as an independent researcher.
I was fortunate to have Prof.\ Lehmann as an advisor during the development of this thesis.
I am also thankful to Prof.\ Dr.\ S{\"o}ren Auer for his support during this thesis.
His insightful guidance helped me to see new ideas when tackling the research problem.
They are both inspiring mentors and continue to lead by example. 
They always challenge me to push ideas and work further, and share their advice and experience on life and research. 
Being able to learn from both of them has been my great fortune.

I would like to thank all the staff members of the Smart Data Analytics (SDA) group at the University of Bonn, for the great time I had.
I really enjoyed the atmosphere and also their friendship.
Special thanks go to Monish Dubey, Harsh Thakkar, Dr.\ Diego Esteves, Mehdi Ali, Ass.\ Prof.\ Maria Maleshkova, Denis Lukovnikov, Dr.\ G{\"{u}}nter Kniesel, Dr.\ Sahar Vahdati, Dr.\ Giulio Napolitano, Hamid Zafar, Debanjan Chaudhuri, Rostislav Nedelchev, Nilesh Chakraborty, Gaurav Maheshwari, Priyansh Trivedi, Mohamed Nadjib Mami, and Debayan Banerjee.
Within our research group, I had the opportunity to be involved and responsible with regard to managing and maintaining some parts of the SANSA project as well as teaching and supervising master students.
I want to thank all my colleagues in the SDA group and am glad to have the opportunity to be part of this group.

Draft versions of the thesis were read by Dr.\ Hajira Jabeen, Dr.\ Damien Graux, and Dr.\ Anisa Rula and I thank them for their valuable feedback and support, which helped to improve the overall quality of the thesis.
I am also grateful for previous collaborations and discussions we had, as a result, it helped me to acquire and improve my academic skills.

As most of the research ideas described in this thesis were implemented, evaluated and integrated into the open-source SANSA project.
I thank everyone working on this project.
In particular, Ivan Emirlov for his DevOps help when it was needed, Lorenz B\"uhmann for his constructive feedback and help while working in SANSA, Claus Stadler, Simon Bin, Patrick Westphal and many more.

I would like to sincerely thank Shendrit Bytyqi and Ali Salihu for their support when we arrived in Germany.
Finally, I would like to express my gratitude to my family and friends, for their persistent support and love and enriching my life beyond my scientific endeavors.
In particular, I thank my lovely wife - Mimoza Sejdiu, for her constant support, sacrifices and understanding in the past years.
Also, I would like to thank my beloved sons - Jon Sejdiu and Nil Sejdiu, for their love and motivation throughout the years of my PhD work.
Thank you all.


\thispagestyle{empty}
{\raggedleft\vfill\itshape\Longstack[l]{%
  This PhD thesis is dedicated \\
  to my lovely wife, Mimoza Sejdiu \\
  and my beloved sons, Jon Sejdiu and Nil Sejdiu. \\
  Love you.
}\par
}
