%------------------------------------------------------------------------------
\chapter{List of Publications}
\label{sec:appendix-publications}
%------------------------------------------------------------------------------
\begin{itemize}
    
\item \emph{Conference Papers (peer reviewed)}

\begin{enumerate}
    
    \item \textbf{Gezim Sejdiu}; Anisa Rula; Jens Lehmann; and Hajira Jabeen, “\href{http://jens-lehmann.org/files/2019/iswc_dist_quality_assessment.pdf}{A Scalable Framework for Quality Assessment of RDF Datasets},” in Proceedings of 18th International Semantic Web Conference (ISWC), 2019. \texttt{URL}:~\url{http://jens-lehmann.org/files/2019/iswc_dist_quality_assessment.pdf}

    \item Claus Stadler; \textbf{Gezim Sejdiu}; Damien Graux; and Jens Lehmann, “\href{http://jens-lehmann.org/files/2019/iswc_sparklify.pdf}{Sparklify: A Scalable Software Component for Efficient evaluation of SPARQL queries over distributed RDF datasets},” in Proceedings of 18th International Semantic Web Conference (ISWC), 2019. \texttt{URL}:~\url{http://jens-lehmann.org/files/2019/iswc_sparklify.pdf}

    \item \textbf{Gezim Sejdiu}; Damien Graux; Imran Khan; Ioanna Lytra; Hajira Jabeen; and Jens Lehmann, “\href{https://gezimsejdiu.github.io/publications/semantic_based_query_paper_SEMANTICS2019.pdf}{Towards A Scalable Semantic-based Distributed Approach for SPARQL query evaluation},” 15th International Conference on Semantic Systems (SEMANTiCS), Research \& Innovation , 2019. \texttt{URL}:~\url{https://gezimsejdiu.github.io/publications/semantic_based_query_paper_SEMANTICS2019.pdf}
    
    \item Natanael Arndt; Sebastian Zänker; \textbf{Gezim Sejdiu}; and Sebastian Tramp. "\href{https://svn.aksw.org/papers/2019/ICWE_JekyllRDF/public.pdf}{Jekyll RDF: Template-Based Linked Data Publication with Minimized Effort and Maximum Scalability}". In 19th International Conference on Web Engineering (ICWE 2019), of ICWE 2019, Daejeon, Korea, June 2019. \texttt{URL}:~\url{https://svn.aksw.org/papers/2019/ICWE_JekyllRDF/public.pdf}

    \item \textbf{Gezim Sejdiu}; Ivan Ermilov; Jens Lehmann; and Mohamed Nadjib-Mami, “\href{http://jens-lehmann.org/files/2018/iswc_distlodstats.pdf}{DistLODStats: Distributed Computation of RDF Dataset Statistics},” in Proceedings of 17th International Semantic Web Conference (ISWC), 2018. \texttt{URL}:~\url{http://jens-lehmann.org/files/2018/iswc_distlodstats.pdf}

    \item Hajira Jabeen; Rajjat Dadwal; \textbf{Gezim Sejdiu}; and Jens Lehmann, "\href{http://jens-lehmann.org/files/2018/ekaw_conod.pdf}{Divided we stand out! Forging Cohorts fOr Numeric Outlier Detection in large scale knowledge graphs (CONOD)}," in 21st International Conference on Knowledge Engineering and Knowledge Management (EKAW'2018), 2018. \texttt{URL}:~\url{http://jens-lehmann.org/files/2018/ekaw_conod.pdf}

    \item Jens Lehmann; \textbf{Gezim Sejdiu}; Lorenz Bühmann; Patrick Westphal; Claus Stadler; Ivan Ermilov; Simon Bin; Nilesh Chakraborty; Muhammad Saleem; Axel-Cyrille Ngomo Ngonga; and Hajira Jabeen, “\href{http://svn.aksw.org/papers/2017/ISWC_SANSA_SoftwareFramework/public.pdf}{Distributed Semantic Analytics using the SANSA Stack},”; in Proceedings of 16th International Semantic Web Conference - Resources Track (ISWC’2017), 2017. \texttt{URL}:~\url{http://svn.aksw.org/papers/2017/ISWC_SANSA_SoftwareFramework/public.pdf}

    \item Ivan Ermilov; Axel-Cyrille Ngonga Ngomo; Aad Versteden; Hajira Jabeen; \textbf{Gezim Sejdiu}; Giorgos Argyriou; Luigi Selmi; Jürgen Jakobitsch; and Jens Lehmann, “\href{https://svn.aksw.org/papers/2017/KESW_BDE_Workflow/public.pdf}{Managing Lifecycle of Big Data Applications},”; in KESW, 2017. \texttt{URL}:~\url{https://svn.aksw.org/papers/2017/KESW_BDE_Workflow/public.pdf}

    \item Sören Auer; Simon Scerri; Aad Versteden; Erika Pauwels; Angelos Charalambidis; Stasinos Konstantopoulos; Jens Lehmann; Hajira Jabeen; Ivan Ermilov; \textbf{Gezim Sejdiu}; Andreas Ikonomopoulos; Spyros Andronopoulos; Mandy Vlachogiannis; Charalambos Pappas; Athanasios Davettas; Iraklis A. Klampanos; Efstathios Grigoropoulos; Vangelis Karkaletsis; Victor Boer; Ronald Siebes; Mohamed Nadjib Mami; Sergio Albani; Michele Lazzarini; Paulo Nunes; Emanuele Angiuli; Nikiforos Pittaras; George Giannakopoulos; Giorgos Argyriou; George Stamoulis; George Papadakis; Manolis Koubarakis; Pythagoras Karampiperis; Axel-Cyrille Ngonga Ngomo; and Maria-Esther Vidal, “\href{http://jens-lehmann.org/files/2017/icwe_bde.pdf}{The BigDataEurope Platform – Supporting the Variety Dimension of Big Data},” in 17th International Conference on Web Engineering (ICWE2017), 2017. \texttt{URL}:~\url{http://jens-lehmann.org/files/2017/icwe_bde.pdf}
     
\end{enumerate}
    
    \item \emph{Demo \& Poster Papers (peer reviewed)}
    
    \begin{enumerate}
    \setcounter{enumi}{9}

    \item Claus Stadler; \textbf{Gezim Sejdiu}; Damien Graux; and Jens Lehmann. "\href{https://gezimsejdiu.github.io/publications/sansa-sparklify-ISWC-demo.pdf}{Querying large-scale RDF datasets using the SANSA framework}".  In Proceedings of 18th International Semantic Web Conference (ISWC), Poster \& Demos, 2019. \texttt{URL}:~\url{https://gezimsejdiu.github.io/publications/sansa-sparklify-ISWC-demo.pdf}

    \item Danning Sui; \textbf{Gezim Sejdiu}; Damien Graux; and Jens Lehmann. "\href{https://gezimsejdiu.github.io/publications/sansa-hubs-and-authorities-transaction-semantics19-poster.pdf}{The Hubs and Authorities Transaction NetworkAnalysis using the SANSA framework}".  In 15th International Conference on Semantic Systems (SEMANTiCS), Poster \& Demos, 2019. \texttt{URL}:~\url{http://tiny.cc/4ukxcz}

    \item Rajjat Dadwal; Damien Graux; \textbf{Gezim Sejdiu}; Hajira Jabeen; and Jens Lehmann. "\href{https://gezimsejdiu.github.io/publications/piping-clustering-eswc19-poster.pdf}{Clustering Pipelines of large RDF POI Data}" in Proceedings of 16th Extended Semantic Web Conference (ESWC), Poster \& Demos, 2019. \texttt{URL}:~\url{https://gezimsejdiu.github.io/publications/piping-clustering-eswc19-poster.pdf}
    
    \item \textbf{Gezim Sejdiu}; Ivan Ermilov; Jens Lehmann; and Mohamed-Nadjib Mami, “\href{http://jens-lehmann.org/files/2018/iswc_statisfy_pd.pdf}{STATisfy Me: What are my Stats?},” in Proceedings of 17th International Semantic Web Conference (ISWC), Poster \& Demos, 2018. \texttt{URL}:~\url{http://jens-lehmann.org/files/2018/iswc_statisfy_pd.pdf}
    
    \item Damien Graux; \textbf{Gezim Sejdiu}; Hajira Jabeen; Jens Lehmann; Danning Sui; Dominik Muhs; and Johannes Pfeffer, “\href{http://jens-lehmann.org/files/2018/semantics_ethereum_pd.pdf}{Profiting from Kitties on Ethereum: Leveraging Blockchain RDF with SANSA},” in 14th International Conference on Semantic Systems, Poster \& Demos, 2018. \texttt{URL}:~\url{http://jens-lehmann.org/files/2018/semantics_ethereum_pd.pdf}
    
    \item Ivan Ermilov; Jens Lehmann; \textbf{Gezim Sejdiu}; Lorenz Bühmann; Patrick Westphal; Claus Stadler; Simon Bin; Nilesh Chakraborty; Henning Petzka; Muhammad Saleem; Axel-Cyrille Ngomo Ngonga; and Hajira Jabeen, “\href{http://jens-lehmann.org/files/2017/iswc_pd_sansa.pdf}{The Tale of Sansa Spark},” in Proceedings of 16th International Semantic Web Conference, Poster \& Demos, 2017 ({\color{darkred}\textbf{Best Demo Award}}). \texttt{URL}:~\url{http://jens-lehmann.org/files/2017/iswc_pd_sansa.pdf}
        
    \end{enumerate}
    
\item \emph{Miscellaneous Papers}

    \begin{enumerate}
    \setcounter{enumi}{15}

    \item Harsh Thakkar; Mohnish Dubey; \textbf{Gezim Sejdiu}; Axel-Cyrille Ngonga Ngomo; Jeremy Debattista; Christoph Lange; Jens Lehmann; Sören Auer; and Maria-Esther Vidal, “\href{http://arxiv.org/pdf/1608.02800}{LITMUS: An Open Extensible Framework for Benchmarking RDF Data Management Solutions},” , 2016. \texttt{URL}:~\url{http://arxiv.org/pdf/1608.02800}

\end{enumerate}

\end{itemize}