%------------------------------------------------------------------------------
\chapter{SANSA Framework Release History}
\label{sec:appendix-sansa-releases}
%------------------------------------------------------------------------------

In the course of the thesis, the following releases of software components were produced (under the \textit{Apache Licence 2.0}).

\begin{itemize}
    \item SANSA\furl{https://github.com/SANSA-Stack} software component related releases\f{This list only includes components that are part of the thesis. 
    The features of SANSA itself are more than those mentioned.}:
    \begin{itemize}
        
        \item \textbf{SANSA v0.7} \textit{2020-01}:
        SPARQL query engine over compressed RDF data.
        Refactoring quality assessment metrics.
        Further alignment and development of the functionality on the Flink module.
        Support for quality assessment over streaming RDF data.
        Bug fixes.
        
        \item \textbf{SANSA v0.6} \textit{2019-06}:
        Support for RDF compression techniques.
        Refactoring semantic-based query engine.
        Support for ingestion of additional RDF formats.
        Align and perfrom evaluations on the Sparklify query engine (see Section~\ref{sec:sparklify-approach} of Chapter~\ref{chapter:scalable_rdf_querying} for more details).
        Bug fixes.
        
        \item \textbf{SANSA v0.5} \textit{2018-12}: 
        Further improvements for Scalable RDF Quality Assessment. 
        Refactoring semantic-based partitioning and RDF Dataset Statistics.
        Bug fixes.
        
        \item \textbf{SANSA v0.4} \textit{2018-06}:
        Further support for Scalable RDF Quality Assessment. 
        Support for ingestion of additional RDF formats.
        Further improvements for semantic-based partitioning.
        Support for graph-based partitioning.
        Query engine on top of semantic-based partitioning.
        Bug fixes.
        
        \item \textbf{SANSA v0.3} \textit{2017-12}: 
        Support for Scalable RDF Quality Assessment(see Chapter~\ref{chapter:dist_quality_assessment} for more details). 
        Support for ingestion of additional RDF formats.
        Support for semantic-based partitioning (see Section~\ref{sec:semantic-based-approach} of Chapter~\ref{chapter:scalable_rdf_querying} for more details).
        
        \item \textbf{SANSA v0.2} \textit{2017-06}: 
        Support for Scalable RDF Dataset Statistics (see Chapter~\ref{chapter:dist_lod_stats} for more details).
        
        \item \textbf{SANSA v0.1} \textit{2016-12}:
        Initial SANSA release. 
        SANSA website and guidelines. 
        Support for reading and writing RDF files in N-Triples format.
    \end{itemize}
    
    \item Big Data Europe Platform\furl{https://github.com/big-data-europe}
    \begin{itemize}
        
    \item \textbf{BDE v1} \textit{2017-11}:
    Integrate SANSA framework with the Big Data Europe Platform.
    Build the stack for the \textit{SC4: Smart Green and Integrated Transport} on the Big Data Europe Integrator Platform.
    
    \item \textbf{BDE v1} \textit{2016-11}:
    Dockerized Big Data Europe Components (e.g Apache Spark, Apache Flink).
    \end{itemize}
    
    \item DL-Learner Framework\furl{https://github.com/SmartDataAnalytics/DL-Learner}
    \begin{itemize}
    
    \item \textbf{DL-Learner v1.4.0} \textit{2019-09}:
    Docker image for DL-Learner.
    \end{itemize}
    
\end{itemize}
